Title goes here

### 2016-10-23 paper/paper.tex
Added subsection technologies

>>>>

Analyzing the entire dataset require a big computational power, therefore use a cluster to perform analyze the data. However, before running on the cluster, we tried the algorithms locally on a small subset of data to test correctness end efficiency and to obtain statistics. For this reason, we used different technologies depending on where we ran the analysis.

On the cluster, we chose to use \textit{Apache Spark} because it is extremely fast while providing an easy interface, resulting suitable for our application. In particular, the \textit{Scala} version was chosen instead of PySpark because of the strongly typing and the functional programming approach. In addition to this, the Java library \textit{libadsb} was used to decode the position messages.

Locally, in addition to \textit{Scala} we used \textit{Haskell} and \textit{Python} as scripting languages. The first one was suitable for data manipulation and algorithms testing, while the second one offers a convenient way to plot data using the library \textit{Matplotlib}.
